Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
post hoc

\subsubsection{Thoroughness: Factors weighed in final choice}
The second metric was the number of factors the participant considered in making their final choice. To determine this, we asked participants to explain why they made their choice(s), and recorded the number of distinct data dimensions mentioned.  An ANOVA revealed a significant effect of interface on the number of such factors mentioned; post-hoc analysis using Tukey-Schiffe adjustments indicated that participants in the DP condition mentioned significantly more dimensions in their final decisions ($M=5.5; SD=1.7$) than those in the control condition ($M=4; SD=1.73$), $F(1,19)=3.95; p<0.10$. A strong significant effect was also observed between participant ID and number of dimensions mentioned, meaning people differed significantly on the number of reasons they gave ($F(19,19)=4.53 p < 0.001$).

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge how well the participant performed their tasks is the number of different data sources the participant consulted during the trial. In this metric, participants used an average of 88\% of data sources provided in the DP case, compared to 80\% in the standard interface, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance in predicting the number of sources consulted ($F(1,19)=0.04$ $p\approx0.10$).

\subsubsection{Effort: External cognition}
Although we did not have an explicit measure of effort for this experiment (such as NASA's TLX \cite{tlx}) the use of paper notes provided an indicator of how much participants had to keep track of during the study.  We found that participants took notes less on average (25\%) with the DP interface than the standard interface (35\%), a difference which approached significance in an ANOVA blocked by participant ($F(1,19)= 8.22; p\approx0.10$).

\begin{figure}[htb]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{\emph{Choice picks per participant trial} - Histogram of number of times each restaurant/university was chosen in DP interface (A condition) in blue/left bars, compared to the Excel/website (B condition) in red/to the right.}
\label{fig:chosen_results}
\end{center}
\end{figure}

\subsubsection{Candidate selection}

Since the tasks were subjective-choice, we could not evaluate the `correctness' of answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we plotted their choice on a histogram for each trial, per task and dataset for both conditions, visible in Figure \ref{fig:chosen_results}.  As can be seen there is considerable variability and no discernible difference in variability between conditions.

>>>>

\subsubsection{Thoroughness: Factors weighed in final choice}
The second metric was the number of factors the participant considered in making their final choice. To determine this, we asked participants to explain why they made their choice(s), and recorded the number of distinct data dimensions mentioned.  A 2-way ANOVA test of the effect of interface and participant ID on the number of factors mentioned revealed a significant effect; post-hoc analysis with Tukey-Schiffe adjustments indicated that participants in the DP condition mentioned significantly more factors in their final decisions ($M=5.5; SD=1.7$) than those in the control condition ($M=4; SD=1.73$), $F(1,19)=3.95; p<0.10$. A strong significant effect was also observed between participant ID and number of dimensions mentioned, meaning some participants mentioned significantly more factors than others ($F(19,19)=4.53; p < 0.001$).

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge the task performance is the number of different data sources consulted during the trial; our rationale for this metric was that more informed decisions derived from more thorough consideration of available data. In this metric, participants used an average of 88\% ($SD=0.13$) of data sources provided in the DP case, compared to 80\% ($SD=0.18$)in the standard interface, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance ($F(1,19)=0.04$ $p\approx0.10$).

\subsubsection{Effort: External cognition}
Although we did not have an explicit measure of effort for this experiment (such as NASA's TLX \cite{tlx}) the use of paper notes provided an indicator of how much information participants had to keep track of during the study.  We found that participants took notes less on average (25\%) with the DP interface than the standard interface (35\%), a difference which approached significance in a 2-way ANOVA blocked by participant ID ($F(1,19)= 8.22; p\approx0.10$).

\begin{figure}[tbp]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{\emph{Choice picks per participant trial} - Histogram of number of times each restaurant/university was chosen in DP interface (A condition) in blue/left bars, compared to the Excel/website (B condition) in red/to the right.}
\label{fig:chosen_results}
\end{center}
\end{figure}

\subsubsection{Candidate selection}
Since the tasks were subjective-choice, we could not evaluate the `correctness' of answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we plotted their choice on a histogram for each trial, per task and dataset for both conditions, visible in Figure \ref{fig:chosen_results}.  As can be seen there is considerable variability and no discernible difference in variability between conditions.
